---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.path  = "man/figures/README-",
  out.width = "60%", 
  # fig.align = "center", 
  fig.show   = "hold", 
  message   = FALSE
)

library(tidyverse)
library(latex2exp)
ggplot2::theme_set(
  theme_bw() + 
    theme(
      legend.position = "bottom", 
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      plot.title = element_text(size = 10, hjust = 0.5)
    )
)

library(here) 
load(here("man", "data", "README-data.RData"))
```

# mhpca

<!-- badges: start -->
<!-- badges: end -->

The `mhpca` package is a tool for conducting Multilevel Hybrid Principal Component Analysis (M-HPCA) proposed in Campos et al. (202?). This package contains the functions necessary to estimate the marginal eigenfunctions, eigenvectors, and product eigencomponents as well as the tools for performing inference.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("emjcampos/mhpca")
```
## Example

Begin by loading the `mhpca` package. 

```{r}
library(mhpca) 
```

The data must be in the following form, with columns labeled `Repetition`, `Group`, `Subject`, `reg`, `func`, and `y`.
```{r}
head(data)
```

Using the `MHPCA_decomp` function, you can estimate the model components.
```{r, eval = FALSE}
MHPCA = MHPCA_decomp(data, fve_cutoff = 0.8, nknots = 5)
```

All of the components can then be plotted and inspected. 
```{r, fig.align = "center"}
ggplot(data.frame(func = unique(data$func), mu = MHPCA$mu)) + 
  geom_line(aes(x = func, y = mu))
```
```{r, fig.align = "center"}
ggplot(MHPCA$eta) + 
  geom_line(aes(
    x = func, y = eta, 
    color = Group, 
    linetype = Repetition, 
    group = interaction(Group, Repetition, reg)
  ))
```


```{r, out.width = "45%"}
data.frame(MHPCA$marg$between$regional$`Group 1`$eigendecomp$vectors[, 1:2]) %>% 
  mutate(reg = unique(data$reg)) %>% 
  pivot_longer(X1:X2, names_to = "v") %>% 
  ggplot() + 
  geom_tile(aes(x = reg, fill = value, y = v)) + 
  labs(
    x = "Region, r", 
    y = element_blank(), 
    fill = TeX("$v^{(1)}_{1k}(r)$"), 
    title = "Group 1, Level 1 Eigenvectors"
  )

data.frame(MHPCA$marg$between$regional$`Group 2`$eigendecomp$vectors[, 1:2]) %>% 
  mutate(reg = unique(data$reg)) %>% 
  pivot_longer(X1:X2, names_to = "v") %>% 
  ggplot() + 
  geom_tile(aes(x = reg, fill = value, y = v)) + 
  labs(
    x = "Region, r", 
    y = element_blank(), 
    fill = TeX("$v^{(1)}_{2k}(r)$"), 
    title = "Group 2, Level 1 Eigenvectors"
  )
```

```{r, out.width = "45%"}
data.frame(MHPCA$marg$within$regional$`Group 1`$eigendecomp$vectors[, 1:2]) %>% 
  mutate(reg = unique(data$reg)) %>% 
  pivot_longer(X1:X2, names_to = "v") %>% 
  ggplot() + 
  geom_tile(aes(x = reg, fill = value, y = v)) + 
  labs(
    x = "Region, r", 
    y = element_blank(), 
    fill = TeX("$v^{(2)}_{1p}(r)$"), 
    title = "Group 1, Level 2 Eigenvectors"
  )

data.frame(MHPCA$marg$within$regional$`Group 2`$eigendecomp$vectors[, 1:2]) %>% 
  mutate(reg = unique(data$reg)) %>% 
  pivot_longer(X1:X2, names_to = "v") %>% 
  ggplot() + 
  geom_tile(aes(x = reg, fill = value, y = v)) + 
  labs(
    x = "Region, r", 
    y = element_blank(), 
    fill = TeX("$v^{(2)}_{2p}(r)$"), 
    title = "Group 2, Level 2 Eigenvectors"
  )
```



```{r, out.width = "45%"}
data.frame(MHPCA$marg$between$functional$`Group 1`$eigendecomp$vectors[, 1:2]) %>% 
  mutate(func = unique(data$func)) %>% 
  pivot_longer(X1:X2, names_to = "phi") %>% 
  ggplot() + 
  geom_line(aes(x = func, y = value, color = phi)) + 
  labs(
    x = "Time, t", 
    y = TeX("$\\phi_{1l}^{(1)}(t)$"), 
    color = TeX("$l$"), 
    title = "Group 1, Level 1 Eigenfunctions"
  )

data.frame(MHPCA$marg$between$functional$`Group 2`$eigendecomp$vectors[, 1:2]) %>% 
  mutate(func = unique(data$func)) %>% 
  pivot_longer(X1:X2, names_to = "phi") %>% 
  ggplot() + 
  geom_line(aes(x = func, y = value, color = phi)) + 
  labs(
    x = "Time, t", 
    y = TeX("$\\phi_{2l}^{(1)}(t)$"), 
    color = TeX("$l$"),
    title = "Group 2, Level 1 Eigenfunctions"
  )
```

```{r, out.width = "45%"}
data.frame(MHPCA$marg$within$functional$`Group 1`$eigendecomp$vectors[, 1:2]) %>% 
  mutate(func = unique(data$func)) %>% 
  pivot_longer(X1:X2, names_to = "phi") %>% 
  ggplot() + 
  geom_line(aes(x = func, y = value, color = phi)) + 
  labs(
    x = "Time, t", 
    y = TeX("$\\phi_{1m}^{(2)}(t)$"), 
    color = TeX("$m$"),
    title = "Group 1, Level 2 Eigenfunctions"
  )

data.frame(MHPCA$marg$within$functional$`Group 2`$eigendecomp$vectors[, 1:2]) %>% 
  mutate(func = unique(data$func)) %>% 
  pivot_longer(X1:X2, names_to = "phi") %>% 
  ggplot() + 
  geom_line(aes(x = func, y = value, color = phi)) +
  labs(
    x = "Time, t", 
    y = TeX("$\\phi_{2m}^{(2)}(t)$"), 
    color = TeX("$m$"),
    title = "Group 2, Level 2 Eigenfunctions"
  )
```

### Performing Bootstrapped Tests 
